Viscous Erosion in Porous Media

### 2018-03-05 docs/methods/erosion_methods.tex
NM
Working over 1-body drag text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Drag}
\label{sec:drag}
With the pressure and shear stress, the drag on a single body with
boundary $\gamma_\ell$ is
\begin{align}
  \FD = \int_{\gamma_\ell} p \nn + \tau \ss \,ds.
  \label{eqn:drag}
\end{align}
The reader may notice an unusual sign convention for pressure in this formula, which is simply due to the normal direction pointing {\em into} the bodies.

@@

In Fig.~\ref{area_drag}(b), we show the drag $F_D$ measured on the body as it erodes. The drag decreases gradually, then takes a nose dive in the final moments when the body vanishes, as is consistent with the logarithmic dependence on lengthscale $L$ in 2D Stokes flow. We also show in the figure the separate contributions of the viscous and the pressure drag. As a final check, are scaling estimates for area change can be rearranged to estimate the viscous drag component
\begin{align}
\label{viscdrag}
F_{\mu} \approx \mean{\atau} L \sim \frac{c_2}{-\log A + c_1 -1}
\end{align}
This scaling law is shown in the figure (red, dotted curve) and shows good agreement with the viscous drag. Of course, \eqref{viscdrag} is less exact than the previous estimates since it does not take into account the normal direction of the surface, only the mean shear stress.

@@

\vsp{20}
Good word: Spontaneous channelization

@@

\vsp{10}
Possible list:
\begin{itemize}
\item Show multiple body simulation with fixed flow rate
\item Then simulation with fixed pressure drop
\item GMRES counts
%
\item $\bigO(5-10)$ bodies
	\begin{itemize}
	\item Area and Drag
	\item Long channels between flat faces
	\end{itemize}
\item $\bigO(50)$ bodies
	\begin{itemize}
	\item Area and Drag
	\end{itemize}
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Drag}
\label{sec:drag}
With the pressure and shear stress, the drag on a single body with
boundary $\gamma_\ell$ is
\begin{align}
  \FFD = \int_{\gamma_\ell} p \nn + \tau \ss \,ds.
  \label{eqn:drag}
\end{align}
The reader may notice an unusual sign convention for pressure in this formula, which is simply due to the normal direction pointing {\em into} the bodies.

@@

In Fig.~\ref{area_drag}(b), we show the horizontal drag $F_D$ measured on the body as it erodes. Note that, in the context of 3D slender-body theory, $F_D$ is drag per unit span. The figure shows the drag to decrease  gradually at first, then abruptly tend to zero in the final moments of the body vanishing. This behavior is consistent with fact that drag vanishes {\em logarithmically} with $L$  in 2D Stokes flow. We also show in the figure the separate contributions of the viscous and the pressure drag. Initially, these two contributions are comparable, with a slightly greater level of pressure drag. However, as the body erodes and assumes a more slender form, the pressure drag vanishes much more rapidly than viscous drag.

As a final check, are scaling estimates for area change can be rearranged to estimate the viscous drag component
\begin{align}
\label{viscdrag}
F_{\mu} \approx \mean{\atau} L \sim \frac{c_2}{-\log A + c_1 -1}
\end{align}
This scaling law is shown in the figure (red, dotted curve) and shows good agreement with the viscous drag. Of course, \eqref{viscdrag} is less exact than the previous estimates since it does not take into account the normal direction of the surface, only the mean shear stress.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.99 \textwidth]{./figs/06plots.pdf}
\caption{\label{fig:06plots} plots to go with 6 body simulation.
}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated from data file 50circ512p5, 
%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1

@@

Good word: Spontaneous channelization

\vsp{3}
Possible list:
\begin{itemize}
\item Show multiple body simulation with fixed flow rate
\item Then simulation with fixed pressure drop
\item GMRES counts
%
\item $\bigO(5-10)$ bodies
	\begin{itemize}
	\item Area and Drag
	\item Long channels between flat faces
	\end{itemize}
\item $\bigO(50)$ bodies
	\begin{itemize}
	\item Area and Drag
	\end{itemize}
\end{itemize}
